### 2019-03-26 5_evaluation.tex
Cut down on the number of load imbalance plots.

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under varying amounts of load imbalance. The
imbalanced workloads are generated by randomly varying the task
durations by $1+(X-0.5)I$
where $X$ is a uniform random variable in the range $[0,1]$ and $I$ is
the degree of imbalance in the range $[0,2]$. The random numbers are
generated with a deterministic pseudo random number generator with a
deterministic seed to ensure that the task durations under all systems
are identical.

>>>>

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance with uniformly distributed task
durations. The task durations are generated with a deterministic
pseudo random number generator with a deterministic seed to ensure
that the task durations under all systems are identical.

### 2019-03-26 e5_imbalance.tex
More text in evaluation.
More text for evaluation section.
Cut down on the number of load imbalance plots.

\begin{figure*}[t]

\subfloat[Imbalance 0.5.\label{fig:efficiency-imbalance-0.5}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/imbalance/efficiency_imbalance_0.5.pdf}
}
\subfloat[Imbalance 1.0.\label{fig:efficiency-imbalance-1.0}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/imbalance/efficiency_imbalance_1.0.pdf}
}

\subfloat[Imbalance 1.5.\label{fig:efficiency-imbalance-1.5}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/imbalance/efficiency_imbalance_1.5.pdf}
}
\subfloat[Imbalance 2.0.\label{fig:efficiency-imbalance-2.0}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/imbalance/efficiency_imbalance_2.0.pdf}
}

\caption{Task granularity vs efficiency for varying load imbalance.\label{fig:metg-imbalance}}
\end{figure*}

>>>>

\begin{figure}[t]

\centering
\includegraphics[width=\columnwidth]{figs/task-bench-results/imbalance/efficiency_imbalance_2.0.pdf}

\caption{Task granularity vs efficiency under load imbalance (nearest pattern, 5 dependencies per task, 4 task graphs, 1 node). Lower is better.\label{fig:efficiency-imbalance}}
\end{figure}
